\documentclass[11pt]{jsarticle}
\usepackage{txfonts}
%\setlength{\textheight}{23cm}
\usepackage{tabularx}
\pagestyle{empty}

\begin{document}

\thispagestyle{empty}

\begin{center}
{\LARGE \textrm{Zin Arai}}\\
\end{center}

\bigskip
\begin{flushleft}
Professor\\
Department of Mathematical and Computing Science\\
School of Computing\\
Tokyo Institute of Technology\\
2-12-1, Ookayama, Meguro-ku, Tokyo 152-8552\\
email: \texttt{zin@c.titech.ac.jp}\\
website: \texttt{http://www.is.c.titech.ac.jp/\textasciitilde zin/}\\
Birth-date and Place: July 22, 1975; Tokyo, Japan
\end{flushleft}

\bigskip
\bigskip

\begin{center}
 {\large \textsf{Education}}
\end{center}
\noindent
\begin{tabularx}{23cm}{ll}
2003 \ Ph.D. & Kyoto University\\
2000 \ M.S. & Kyoto University\\
1998 \ B.S. & Kyoto University\\
\end{tabularx}

\bigskip
\bigskip

\begin{center}
 {\large \textsf{Employment}}
\end{center}
\noindent
\begin{tabularx}{23cm}{ll}
2023 Apr. - Present & Professor\\
& Tokyo Institute of Technology\\

2017 Apr. - 2023 Apr. & Professor\\
& Chubu University Academy of Emerging Sciences\\

2011 Oct. - 2017 Mar. & Associate Professor\\
& Department of Mathematics, Hokkaido University \\

2008 Aug. - 2011 Sep. & Assistant Professor\\
& Creative Research Institution, Hokkaido University \\

2007 Sep. - 2011 Mar. & PRESTO Researcher\\
& Japan Science and Technology Agency \\

2003 July - 2008 July & Assistant Professor\\
& Department of Mathematics, Kyoto University \\

2003 Apr - Jun & JSPS Postdoctoral Fellow\\ 
\end{tabularx}


\newpage

\begin{center}
 {\large \textsf{Activities}}
\end{center}

\hspace*{-4mm}
\begin{tabularx}{23cm}{ll}
2020 Jan. - Present\phantom{hog} & Executive Committee,\\
& East Asia Section of Society for Industrial and Applied Mathematics\\

2021 Jan. - Present & Editorial Board,
SIAM Journal of Applied Dynamical Systems\\
\end{tabularx}

\bigskip
\bigskip

\begin{center}
 {\large \textsf{Selected Publications}}
\end{center}

\begin{itemize}

\item[{\sf [1]}] 
H. Koda, \underline{Z. Arai}, and I. Matsuda, 
Agent-based simulation for reconstructing social structure by observing collective movements with special reference to single-file movement, 
{\it PLOS ONE}, December 3, 2020.
https://doi.org/10.1371/journal.pone.0243173

\smallskip

\item[{\sf [2]}]
T. Tsutsumi, Y. Ono, \underline{Z. Arai}, and T. Taketsugu, 
Visualization of the Dynamics Effect: Projection of on-the-Fly Trajectories to the Subspace Spanned by the Static Reaction Path Network,
{\it J. Chem. Theory Comput.} {\bf 16(7)} (2020), 4029–-4037.
https://doi.org/10.1021/acs.jctc.0c00018

\smallskip

\item[{\sf [3]}] 
\underline{Z. Arai}, Y. Ishii and H. Takahasi, 
Boundary of the horseshoe locus for the H\'{e}non family, 
{\it SIAM Journal on Applied Dynamical Systems} {\bf 17-3} (2018), 2234-2248,
DOI: 10.1137/18M1174684

\smallskip

\item[{\sf [4]}] T. Tsutsumi, Y. Ono, \underline{Z. Arai} and T. Taketsugu, 
Visualization of the intrinsic reaction coordinate and global reaction route map by classical multidimensional scaling, 
{\it J. of Chem. Theory Comput.} {\bf 14(8)} (2018), 4263--4270,
DOI: 10.1021/acs.jctc.8b00176

\smallskip

\item[{\sf [5]}] 
\underline{Z. Arai} and Y. Ishii,
On parameter loci of the H\'{e}non family, 
{\it Communications in Mathematical Physics} {\bf 361(2)} (2018), 343--414, 
DOI: 10.1007/s00220-018-3174-0

\item[{\sf [6]}] 
{\underline{Z. Arai}}, 
On loops in the hyperbolic locus of the complex H\'enon map and their monodromies,
{\it Physica D} {\bf 334} (2016), 133--140.

\smallskip

\item[{\sf [7]}] 
{\underline{Z. Arai}}, 
{Decomposition and clustering for the visualization of dynamical systems}, 
{\it Mathematical Progress in Expressive Image Synthesis I}, Springer (2014), 13--20.

\smallskip

\item[{\sf [8]}] 
{\underline{Z. Arai}}, 
{A rigorous numerical algorithm for computing the linking number of links},
{\it  Nonlinear Theory and Its Applications} {\bf 4:1} (2013), 104--110.

\smallskip

\item[{\sf [9]}] 
{\underline{Z. Arai}}, M. Gameiro, T. Gedeon, H. Kokubu, K. Mischaikow, and H. Oka, 
{Graph-based topological approximation of saddle-node bifurcation in maps}, 
{\it RIMS Kokyuroku Bessatsu}, B 31 (2012), 225--241.

\smallskip

\item[{\sf [10]}] 
    \underline{Z. Arai}, H. Kokubu and I. Obayashi, 
    Capturing the global behavior of dynamical systems with Conley-Morse graphs,
    {\it Advances in Cognitive Neurodynamics} (III) (2012), Springer, 665--672.

    \smallskip

\item[{\sf [11]}] 
{\underline{Z. Arai}, K. Hayashi and Y. Hiraoka}, 
{Mayer-Vietoris sequences and coverage problems in sensor networks},
{\it Japan Journal of Industrial and Applied Mathematics} {\bf 28} (2011), 237--250,

\smallskip
\item[{\sf [12]}] 
  \underline{Z. Arai}, W. Kalies, H. Kokubu, K. Mischaikow, H. Oka and P. Pilarczyk, 
  A Database Schema for the Analysis of Global Dynamics,
  AIP Conference Proceedings {\bf 1168} (2009), 918, https://doi.org/10.1063/1.3241632 

\smallskip

\item[{\sf [13]}] 
{\underline{Z. Arai}, W. Kalies, H. Kokubu, K. Mischaikow, H. Oka and P. Pilarczyk}, 
{A database schema for the global dynamics of multi-parameter systems},
{\it SIAM Journal on Applied Dynamical Systems}
{\bf 8} (2009), 757--789.

\smallskip

\item[{\sf [14]}] 
{\underline{Z. Arai}, H. Kokubu and P. Pilarczyk}, 
{Recent development in rigorous computational methods in dynamical systems},
{\it Japan Journal of Industrial and Applied Mathematics}
{\bf 26} (2009), 393--417.

\smallskip

\item[{\sf [15]}] 
\underline{Z. Arai}, 
Hyperbolicity, stability and monodromy of dynamical systems, 
{\it PAMM}, {\bf 7} (2007), 
Special Issue: Sixth International Congress on Industrial Applied Mathematics (ICIAM07).

\smallskip

\item[{\sf [16]}]
{\underline{Z. Arai}}, 
{On hyperbolic plateaus of the H\'{e}non map},
{\it Experimental Mathematics}
{\bf 16:2} (2007), 181--188.

\smallskip

\item[{\sf [17]}] 
{\underline{Z. Arai}} and K. Mischaikow, 
{Rigorous computations of homoclinic tangencies},
{\it SIAM Journal of Applied Dynamical Systems}
{\bf 5} (2006), 280--282.

 \smallskip

\item[{\sf [18]}]
{\underline{Z. Arai}}, 
{Equivalence of graded module braids and interlocking sequences},
{\it Journal of Mathematics of Kyoto University} 
{\bf 43} (2003), 441--449. 

 \smallskip

\item[{\sf [19]}] 
{\underline{Z. Arai}},
{Tangencies and the Conley index},
{\it Ergodic Theory \& Dynamical Systems} 
{\bf 22} (2002), no. 4, 973--999.

\end{itemize}

\end{document} 
